\documentclass[12pt]{amsart}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amscd}

\usepackage[margin=1in]{geometry}

\usepackage{csquotes}
\usepackage{enumitem}
\usepackage{nameref}

\title{Continuous Real-Valued Functions}
\author{Arden Rasmussen}
\date{\today}

\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

\newcommand{\sep}[1]{\noindent\rule{\textwidth}{#1pt}}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\No}{\mathbb{N}_0}

\begin{document}
\maketitle
\section{Basic Properties}%
\label{sec:Basic Properties}

Suppose that $f,g:\Omega\rightarrow\R$ are continuous. Show that the following
functions are also continuous:

\begin{enumerate}[label=(\alph*)]
  \item $f+g$ and $f-g$
  \item $f \cdot g$
  \item $c \cdot f$, where $c$ is some constant
  \item $f/g$, provided $g \neq 0$
\end{enumerate}

\sep{2}

\subsection{}%
\label{sub:1a}

\begin{proof}
  Let $\varepsilon>0$. We assume $f,g:\Omega\rightarrow\R$ are continuous.
  Assmue that the sequence $x_n\rightarrow x_\ast$. Let $N_f,N_g\in\N$ such
  that
  \begin{align*}
    n>N_f&\implies|f(x_n)-f(x_\ast)|<\frac{\varepsilon}{2}\\
    n>N_g&\implies|g(x_n)-g(x_\ast)|<\frac{\varepsilon}{2}
  \end{align*}
  Take $N=max({N_f,N_g})$. Thus when $n>N$ both of the previous statements are
  true. Consider 
  \begin{align*}
    &|(f+g)(x_n)-(f+g)(x_\ast)|\\
    &=|f(x_n)+g(x_n)-f(x_\ast)-g(x_\ast)|\\
    &=|(f(x_n)-f(x_\ast))+(g(x_n)-g(x_\ast))|\\
    &\leq|f(x_n)-f(x_\ast)|+|g(x_n)-g(x_\ast)|\\
    &<\frac{\varepsilon}{2} + \frac{\varepsilon}{2}\quad \text{when}\ n>N\\
    &=\varepsilon
  \end{align*}
  Now we can conclude that $(f+g)(x_n)\rightarrow(f+g)(x_\ast)$ and thus $f+g$
  must be continuous.
  Now consider
  \begin{align*}
    &|(f-g)(x_n)-(f-g)(x_\ast)|\\
    &=|f(x_n)-g(x_n)-f(x_\ast)+g(x_\ast)|\\
    &=|(f(x_n)-f(x_\ast))+(g(x_\ast)-g(x_n))|\\
    &\leq|f(x_n)-f(x_\ast)|+|g(x_\ast)-g(x_n)|\\
    &=|f(x_n)-f(x_\ast)|+|g(x_n)-g(x_\ast)|\\
    &<\frac{\varepsilon}{2}+\frac{\varepsilon}{2}\quad \text{when}\ n>N\\
    &=\varepsilon
  \end{align*}
  We can see that $(f-g)(x_n)\rightarrow(f-g)(x_\ast)$ and thus $f-g$ must be
  continuous.
\end{proof}

\subsection{}%
\label{sub:1b}

\begin{proof}
  Let $\varepsilon>0$. We define $M$ such that
  \begin{align*}
    M=max\left(\left\{|f(x_\ast)|,|g(x_\ast)|,1\right\}\right)
  \end{align*}
  Let $N\in\N$ such that
  \begin{align*}
    n>N\implies\begin{cases}
      |f(x_n)-f(x_\ast)|<\frac{\varepsilon}{3M}\\
      |g(x_n)-g(x_\ast)|<\frac{\varepsilon}{3M}\\
    \end{cases}
  \end{align*}
  Consider
  \begin{align*}
    &|(f \cdot g)(x_n)-(f \cdot g)(x_\ast)|\\
    &=|f(x_n)g(x_n)-f(x_\ast)g(x_\ast)|\\
    &=|f(x_n)g(x_n)-f(x_n)g(x_\ast)+f(x_n)g(x_\ast)-f(x_\ast)g(x_\ast)|\\
    &=|f(x_n)(g(x_n)-g(x_\ast))+g(x_\ast)(f(x_n)-f(x_\ast))|\\
    &\leq|f(x_n)(g(x_n)-g(x_\ast))|+|g(x_\ast)(f(x_n)-f(x_\ast))|\\
    &=|f(x_n)||g(x_n)-g(x_\ast)|+|g(x_\ast)||f(x_n)-f(x_\ast)|\\
    &\text{Since $|g(x_\ast)|\leq M$ and $|f(x_n)|<M+\frac{\varepsilon}{3M}$}\\
    &<\left(M+\frac{\varepsilon}{3M}\right)|g(x_n)-g(x_\ast)|+M|f(x_n)-f(x_\ast)|\\
    &<\left(M+\frac{\varepsilon}{3M}\right)\frac{\varepsilon}{3M}+M\frac{\varepsilon}{3M}\quad\text{when}\
    n>N\\
    &=\frac{\varepsilon}{3}+\frac{\varepsilon^2}{9M^2}+\frac{varepsilon}{3}\\
    &\text{Since $M\geq 1$ then we know }
    &<\frac{\varepsilon}{3}+\frac{\varepsilon}{3}+\frac{\varepsilon}{3}\\
    &=\varepsilon
  \end{align*}
\end{proof}

\section{Composition}%
\label{sec:composition}

Suppose $f:U\rightarrow\R$ and $g:V\rightarrow\R$ are continuous, and that
$f(U)\subset V$. Show that $g\circ f:U\rightarrow\R$ is continuous.

\sep{2}

\section{Examples}%
\label{sec:examples}

\begin{enumerate}[label=(\alph*)]
  \item Show that all polynomial functions are continuous
  \item Show that $f:(0,\infty)\rightarrow\R$ given by $f(x)=\frac{1}{x}$ is
    continuous.
\end{enumerate}

\sep{2}

\section{Non-Example}%
\label{sec:non_example}

Let $\sigma:\R\rightarrow\R$ is given by

\begin{equation*}\label{eq:4.1}
  \sigma(x)=\begin{cases}
    1 & \text{if}\ x\in\Q \\
    0 & \text{if}\ x\notin\Q
  \end{cases}
\end{equation*}

Show that $\sigma$ is not continuous.

\sep{2}

\section{The Square Root Function}%
\label{sec:the_square_root_function}

Consider the square root function $f:[0,\infty)\rightarrow\R$ given by
$f(x)=\sqrt{x}$.

\begin{enumerate}[label=(\alph*)]
  \item Show that the square root function is \textit{strictly increasing},
    meaning that
    \begin{equation*}\label{eq:5a.0}
      a<b\implies\sqrt{a}<\sqrt{b}
    \end{equation*}
  \item Show that the square root function is continuous.
\end{enumerate}

\sep{2}

\section{Intermediate Value Theorem}%
\label{sec:intermediate_value_theorem}

Suppose that $f:[a,b]\rightarrow\R$ is continuous and that $y_\ast$ is between
$f(a)$ and $f(b)$. Prove that there exists $x_\ast\in[a,b]$ such that
$f(x_\ast) = y_\ast$.

\sep{2}

\section{$\varepsilon - \delta$ Criterion for Continuity}%
\label{sec:_varepsilon_delta_criterion_for_continuity}

Show that the following are equivalent:

\begin{enumerate}[label=(\alph*)]
  \item $f:\Omega\rightarrow\R$ is continuous at $x_\ast\in\Omega$.
  \item For each $\varepsilon>0$ there exists $\delta>0$ such that for all
    $x\in\Omega$ we have
    \begin{equation*}\label{eq:7b.0}
      |x-x_\ast|<\delta\implies|f(x)-f(x_\ast)|<\varepsilon
    \end{equation*}
\end{enumerate}

Then illustrate the second condition with a picture.

\sep{2}

\section{Example}%
\label{sec:example}

Show directly that the function $f:\R\rightarrow\R$ given by $f(x)=x^2$
satisfies condition (b) above at $x_\ast=2$.

\sep{2}

\section{Examples}%
\label{sec:examples}

\begin{enumerate}[label=(\alph*)]
  \item Show that $f:[0,1]\rightarrow\R$ given by $f(x)=x^2$ is uniformly
    continuous.
  \item Show that $f:[1,\infty)\rightarrow\R$ given by $f(x)=\frac{1}{x}$ is uniformly
    continuous.
  \item Show that $f:(0,\infty)\rightarrow\R$ given by $f(x)=\frac{1}{x}$ is
    not uniformly continuous.
\end{enumerate}

\sep{2}

\end{document}
