\documentclass[12pt]{amsart}
\usepackage{amsmath}
\usepackage{csquotes}
\usepackage{enumitem}
\usepackage{hanging}
% \usepackage[margin=1in]{geometry}

\title{Discussion 1}
\author{Arden Rasmussen}
\date{\today}

\begin{document}
\maketitle

\par\noindent\rule{\textwidth}{0.4pt}

\begin{hangparas}{.25in}{1}
  Hurwit, Jeffrey. "Homeric Questions." In \textit{The Art and Culture of Early
  Greece: 1100-480 B.C.}, 85-106. Ithaca and London: Cornel Univsersity Press,
  1985
\end{hangparas}

\par\noindent\rule{\textwidth}{0.4pt}

There was initially the debate as to weather Homers works were his own or a
collection, but that has shifted to if he was the origin or just transcribed
oral tales. Hurwit thinks that there must have been different authors for the
\textit{Iliad} and the \textit{Odyssey}, because of the stark contrast between
the writing styles, and the characteristics of the heroes. He also noted that
moods of the epics differ greatly.  The \textit{Odyssey} seems to be
self-reflexive, it makes note that poetry is a major theme. One thought for
this is that since the \textit{Iliad} exists, then more emphasis was placed on
matching the quality of the poem.

Was writing developed for poetry? Several early writings are poetic, but it is
doubtful that the \textit{Iliad} was written out.

He also notes that there are many similarities between the Dipylon Style of the
geometric period, and Homers writing. The potters found it hard to mix the
patterns with the content.  This similarity is demonstrated in the symmetry and
patterns that arise. A final note is that both the Dipylon style and Homers
writing leave nothing out of view, everything is in the foreground, and laid
out for the viewers.

The argument for different authors, intrigues me less, as I don't see how that
would change anything, the writing is still the same. I am much more fascinated
in the similarity brought between the geometric period pottery, and the
writing style of Homer. This sheds new light on the structure of the writing
for me, and I find it very interesting.

\textbf{How does different authors/multiple authors really effect our
interpretation of the \textit{Iliad} and \textit{Odyssey}?  }

\par\noindent\rule{\textwidth}{0.4pt}

Words: 259

\par\noindent\rule{\textwidth}{0.4pt}

\end{document}
