\documentclass{subfile}
\begin{document}

\section{Chapter 15}

\subsection{Traveling Waves}

\begin{align}
	v_{string} &= \sqrt{\frac{F_{T}}{\mu}} \label{15:tw:1}\\
	v_{sound} &= \sqrt{\frac{B}{\rho}} \label{15:tw:2}\\
	v_{sound} &= 343\frac{m}{s} \label{15:tw:3}\\
	c &= 3.00x10^{8}\frac{m}{s} \label{15:tw:4}\\
	r &= \frac{v_{2} - v_{1}}{v_{2} + v_{1}} \label{15:tw:5}\\
	\tau &= \frac{2v_{2}}{v_{2} + v_{1}} \label{15:tw:6}\\
	\frac{\partial^{2}y}{\partial x^{2}} &= \frac{1}{v^{2}} * \frac{\partial^{2}y}{\partial^{2}} \label{15:tw:7}
\end{align}

\begin{enumerate}
	\item[\eqref{15:tw:1}] Speed of wave on a string, where $v$ is the velocity of the wave, $F_{T}$ is the tension force, and $\mu$ is the linear density of the string.
	\item[\eqref{15:tw:2}] Speed of sound wave in a fluid, where $v$ is the velocity of the wave, $B$ si the Bulk Modulus,  and $\rho$ is the volume density of the fluid.
	\item[\eqref{15:tw:3}] Constant of the speed of sound in air.
	\item[\eqref{15:tw:4}] Constant of the spee dof light/electormagnetic waves in vacuum.
	\item[\eqref{15:tw:5}] Reflection coefficient equation, where $r$ is the reflection coefficient, $v_{1}$ is the wave velocity in the first region, and $v_{2}$ is the wave velocity in the second region.
	\item[\eqref{15:tw:6}] Transmission coefficient equatoin, where $\tau$ is the transmission coefficient, $v_{1}$ is the wave velocity in the first region, and $v_{2}$ is the wave velocity in the second region.
	\item[\eqref{15:tw:7}] Wave equation for a traveling wave.
\end{enumerate}

\subsection{Harmonic Traveling Waves}

\begin{align}
	y(x,t) &= A sin (kx \pm \omega t) \label{15:htw:1}\\
	&= A sin(k(x \pm vt)) \label{15:htw:2}\\
	k &= \frac{2\pi}{\lambda} \label{15:htw:3}\\
	v &= f\lambda \label{15:htw:4}\\
	&= \frac{\omega}{k} \label{15:htw:5}\\
	\omega &= s\pi f \label{15:htw:6}\\
	&= \frac{2\pi}{T} \label{15:htw:7}\\
	P_{avg} &= \frac{1}{2}\mu v \omega^{2}A^{2} \label{15:htw:8}\\
	I &= \frac{P_{avg}}{A} \label{15:htw:9}\\
	\beta &= (10dB)log_{10}\left( \frac{I}{I_{0}}\right) \label{15:htw:10}\\
	I_{0} &= 10^{12}\frac{W}{m^{2}} \label{15:htw:11}
\end{align}

\begin{enumerate}
	\item[\eqref{15:htw:1}] Wave equation, where $y$ is the height, $x$ is the position, $t$ is the time, $A$ is the amplitude, $k$ is the wave number, and $\omega$ is the angular frequency. Use $+$ for waves traveling in the $+x$ direction, and use $-$ for waves traveling in the $-x$ direction.
	\item[\eqref{15:htw:2}] Wave equation, where $A$ is the amplitude, $k$ is the wave number, $x$ is the position, $v$ is the wave speed, and $t$ is the time.
	\item[\eqref{15:htw:3}] Wave number equation, where $k$ is the wave number, and $\lambda$ is the wave length.
	\item[\eqref{15:htw:4}] Wave speed equation, where $v$ is the wave speed, $f$ is the frequency, and $\lambda$ is the wavelenght.
	\item[\eqref{15:htw:5}] Wave speed equaiton, where $\omega$ is the angular frequency, and $k$ is the wave number.
	\item[\eqref{15:htw:6}] Angular frequency equation, where $\omega$ is the angular frequency, and $f$ is the frequency
	\item[\eqref{15:htw:7}] Angular frequency equation, where $T$ is the period.
	\item[\eqref{15:htw:8}] Average power for a harmonic wave on a string, where $P_{avg}$ is average power, $\mu$ is the linear density of the string, $v$ is the velocity of the string, $\omega$ is the angular frequency, and $A$ is the amplitude.
	\item[\eqref{15:htw:9}] Intensity of a harmonic wave, where $I$ is the intensity, $P_{acg}$ is the average power, and $A$ is the amplitude.
	\item[\eqref{15:htw:10}] Intensity of a wave in dB, where $\beta$ is the intensity in dB, $I$ is the intensity, and $I_{0}$ is a constant.
	\item[\eqref{15:htw:11}] Constant of $I_{0}$.
\end{enumerate}

\subsection{Doppler Shifts}

\begin{align}
	f_{r} &= \frac{v \pm u_{r}}{\lambda} \label{15:ds:1}\\
	\lambda &= \frac{v \pm u_{s}}{f_{s}} \label{15:ds:2}\\
	f_{r} &= \frac{v \pm u_{r}}{v \pm u_{s}}f_{s} \label{15:ds:3}\\
	\frac{f_{r}}{v \pm u_{r}} &= \frac{f_{s}}{v \pm u_{s}} \label{15:ds:4}\\
	u &\ll v\quad Where\ u = u_{s} \pm u_{r} \label{15:ds:5}\\
	\frac{\Delta f}{f_{s}} &\approx \pm \frac{u}{v} \label{15:ds:6}
\end{align}

\begin{enumerate}
	\item[\eqref{15:ds:1}] Frequency received when the receiver is moving, where $f_{r}$ is the frequency, $v$ is the speed of the wave, $u_{r}$ is the speed of the receiver, and $\lambda$ is the wavelength.
	\item[\eqref{15:ds:2}] Wavelength of wave when the source is moving, where $\lambda$ is the wavelength, $v$ is the speed of the wave, and $u_{s}$ is the speed of the source.
	\item[\eqref{15:ds:3}] Frequency if either the source or receiver is moving, where $f_{r}$ is the frequency received, $v$ is the speed of the wave, $u_{r}$ is the speed of the receiver, $u_{s}$ is the speed of the source, and $f_{s}$ is the frequency emited by the source. Choose signs that give and up-shift in frequency for an approaching source or receiver, and vice versa. 
	\item[\eqref{15:ds:4}] Equation relating frequency of source and receiver, where $f_{r}$ is the frequency received, $v$ is the speed of the wave, $u_{r}$ is the speed of the recever, $f_{s}$ is the frequency emited by the source, and $u_{s}$ is the speed of the source.
	\item[\eqref{15:ds:5}] For small speed of the source and receiver comparitivly to the wave, the estimation is true, where $u$ is the speed of the source and receiver, $v$ is the speed of the wave, $u_{s}$ is the speed of the source, and $u_{r}$ is the speed of the receiver.
	\item[\eqref{15:ds:6}] This approximaition only holds if \eqref{15:ds:5} is true, then this is true, where $\Delta f$ is the change in frequency, $f_{s}$ is the frequency emited by the source, $u$ is the velocity of the source and reciver from \eqref{15:ds:5}, and $v$ is the velocity of the wave.
\end{enumerate}
\end{document}
