\documentclass{subfile}
\begin{document}
\section{Chapter 16}

\subsection{Superposition and Standing waves}

\begin{align}
	y &= y_{1} + y_{2} \label{16:ssw:1}\\
	&= y_{0}sin\left( kx-\omega t\right) + y_{0} sin\left( kx-\omega t + \delta \right) \label{16:ssw:2}\\
	&= \left( 2y_{0}cos\left(\frac{\delta}{2}\right)\right)sin\left(kx-\omega t + \frac{\delta}{2}\right) \label{16:ssw:3}\\
	\delta &= k\Delta x \label{16:ssw:4}\\
	& = 2\pi \frac{\Delta x}{\lambda} \label{16:ssw:5}\\
	\lambda_{n} &= \frac{2L}{n}\quad n=1,2,3,4... \label{16:ssw:6}\\
	\lambda_{n} &= \frac{4L}{n}\quad n=1,3,5,7... \label{16:ssw:7}
\end{align}

\begin{enumerate}
  \item []The superposition of two waves with the same amplitude, wave number, andfrequency, but phase difference $\delta$, results in a harmonic wav eof the same wave number and frequency, but differing in phase and amplitude from each of the two waves.
	\item[\eqref{16:ssw:1}] The amplitude of the wave is the sum of the amplitudes of each wave, where $y$ is the resultant value, $y_{1}$ is the value of the first wave, and $y_{2}$ is the value of the second wave.
	\item[\eqref{16:ssw:2}] Superposition of two waves, where $y_{0}$ is the amplitude of the source, $k$ is the wave number, $x$ is the position, $\omega$ is the angular frequency, $t$ is the time, and $\delta$ is the phase difference.
	\item[\eqref{16:ssw:3}] Superposition of two waves, where $y_{0}$ is the amplitude of the source, $\delta$ is the phase difference, $k$ is the wave number, $x$ is the position, $\omega$ is the angular frequency, and $t$ is the time.
	\item[\eqref{16:ssw:4}] Phase difference due to path difference, where $\delta$ is the phase difference, $k$ is the wave number, and $\Delta x$ is the difference between distances from the two sources. 
	\item[\eqref{16:ssw:5}] Phase difference due to path difference, where $\Delta x$ is the difference between the distances from the two sources, and $\lambda$ is the wavelength.
	\item[\eqref{16:ssw:6}] Wavelength for standing wave fixed at both ends, where $n$ is the wave number, $\lambda_{n}$ is the wavelength for that wave number, and $L$ is the length of string.
	\item[\eqref{16:ssw:7}] Wavelength for standing wave fixed at one end, where $n$ is the wave number, $\lambda_{n}$ is the wavelength for that wave number, and $L$ is the length of string. 
\end{enumerate}
\end{document}
