\documentclass[12pt]{article}

\usepackage[head=29pt, margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\lhead{\large{Columbia River Dams}}
\rhead{Arden Rasmussen\\01 May 2017}

\linespread{1.5}

\begin{document}
\section{Description}
\begin{itemize}
  \item The dams are an important part of the history of the Northwest and of Oregon.
  \item The dams produced huge amounts of electricity and made water readily available.
  \item Farmers were distributed land to use, and provided with subsidized water.
    \begin{itemize}
      \item These small farms were not successful.
      \item Successful ones wanted to grow.
      \item Less successful ones could not grow, or afford new and more efficient tools.
      \item Small farmers began to disappear, despite the initial plans to support them.
    \end{itemize}
  \item The dams also drew industries.
    \begin{itemize}
      \item The main industry drawn was aluminum smelting.
      \item The aluminum smelting produced a lot of pollution.
      \item These industry mills have begun to move away.
    \end{itemize}
  \item The dams destroyed many homes of the native Americans, without any compensation.
  \item The dams also wreaked native fish habitats.
  \item These last two have not changed over time.
\end{itemize}
\section{Questions}
\begin{itemize}
  \item What were the benefits and the costs of the dams when they were first being constructed?
  \item What are the benefits of the costs of the dams in current times?
  \item Do the benefits still outweigh the costs of the dams?
\end{itemize}
\section{Voices}
\begin{itemize}
  \item Corporations
  \item Native Americans
  \item Environmentalists
  \item Employees
  \item Small farmers
  \item Corporate farms
  \item Dam Organizers/Planners
\end{itemize}
\section{Results}
I found that:
\begin{itemize}
  \item I found that when the dams were first constructed, they were extremely beneficial, and help develop the region in several ways.
  \item I also found that as time has passed, the value of the dams has dropped, and they have become less useful in the past few years.
  \item I think that the utility of the dams has lost some of its importance, and so they no longer are more beneficial than they cost.
  \item So some of the dams could be removed, while still maintaining much of the utility from remaining dams.
\end{itemize}
\end{document}
