\documentclass{amsart}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{cite}

\title{Independent Study Group Report}
\author{Arden Rasmussen, Sean Richardson, Adriana Rogers }
\date{Spring 2019}

\begin{document}

\maketitle

\section{Introduction}
% ADRIANA

\section{Optimization}
% SEAN
%this is a math problem, and these are the CS ways to solve it.

\section{Neural Networks}
%ADRIANA + ARDEN

\subsection{Architecture}

\subsection{Propagation}
%computational graph
%loss functions -- harken back to optimization section

\subsection{Convolutional Layers}

\section{Genetic Algorithms}
%ADRIANA

\subsection{Initialization}

\subsection{Evaluation}

\subsection{Selection}

\subsection{Recombination}

\subsection{Mutation}

\subsection{Replacement}

\section{Snake Project}

We decided to apply the strategies of neural networks and genetic algorithms in
order to train an AI to play a game of snake. This sample implementation
provides a good testing ground for utilizing these strategies. The search space
for an AI to play snake is sufficiently large, that it is possible to see
improvements in the performance of the AI, but it is small enough that those
improvements do not take long.
% ARDEN

\subsection{Game Set-Up and Rules}

The first step of the process was to construct the game itself. The game
itself is very simple. A player controls a snake on a grid. The snake is
trying to eat food (an apple), and every time the snake eats a piece of food,
it grows in length by one. If the snake runs into the walls or itself, it dies.

We decided to split the game into four main functions.
\begin{enumerate}
  \item \textit{Initialize:} This function initializes the game state. This
    includes the position of the apple, the position of the snake, and the size
    of the grid. For most of our testing we defaulted to a grid of size 20.
  \item \textit{Get Move:} This function provides provides some interface with
    the current game state, and retrieves a direction to move in. This
    interface can either be a user input, or it could be some AI process.
  \item \textit{Update:} This function updates the game state provided with
    the direction to move in. This function moves the snake, and if it eats an
    apple, it extends the snake by one, and spawns a new apple on the grid.
  \item \textit{Valid:} This function checks if the current game state is
    valid. This is where we test to see if the snake has run into itself, or a
    wall.
\end{enumerate}

The basic structure of the snake program is to execute function 1 once, and
then while the game state is valid execute functions 2-3. The final part of the
game is the scoring system. Each update without dying increases the score by
1, and each apple eaten increases the score by 1000.

\begin{figure}[htpb]
  \begin{center}
    \begin{tikzpicture}[scale=0.75, transform shape,
      box/.style={rectangle,draw=black,thick,minimum size=1cm}]
      \foreach \x in {0,...,10}{
        \foreach \y in {0,...,10}{
          \node[box] at (\x,\y){};
        }
      }
      \node[box,fill=green] at (7,3){};
      \node[box,fill=black] at (5,6){};
      \node[box,fill=black] at (5,7){};
      \node[box,fill=black] at (5,8){};
      \node[box,fill=black] at (6,8){};
      \node[box,fill=black] at (7,8){};
      \node[box,fill=black] at (7,7){};
      \node[box,fill=red] at (7,6){};
    \end{tikzpicture}
  \end{center}
  \caption{Example game state for a snake game, here black denotes the snake
  body, green denotes the apple, and red denotes the snake head.}
  \label{fig:snake_game}
\end{figure}


Using this basic structure of the snake game, we determine that the
optimization problem at hand is to maximize the score of the game. Now we
construct the architecture of a neural network and genetic algorithm to solve
this optimization problem.

\subsection{Neural Network Structure}

Since any neural network requires a specific number of input, we decided on
utilizes rays. For each of the four directions from the snake, we cast a ray.
The ray will tell the neural network how far away something is in that
direction. For this we case three different rays in each direction.
\begin{enumerate}
  \item Apple Ray. Tells the network how far away the apple is in that
    direction, if at all.
  \item Snake Ray. Tells the network how far away the snake body is in that
    direction, if at all.
  \item Wall Ray Tells the network how far away the wall is in that direction.
\end{enumerate}
The casting of these rays can be seen in figures \ref{fig:snake_rays}.

\begin{figure}[htpb]
  \begin{center}
    \begin{tikzpicture}[scale=0.75, transform shape,
      box/.style={rectangle,draw=black,thick,minimum size=1cm}]
      \foreach \x in {0,...,10}{
        \foreach \y in {0,...,10}{
          \node[box] at (\x,\y){};
        }
      }
      \node[box,fill=green] at (7,3){};
      \node[box,fill=black] at (5,6){};
      \node[box,fill=black] at (5,7){};
      \node[box,fill=black] at (5,8){};
      \node[box,fill=black] at (6,8){};
      \node[box,fill=black] at (7,8){};
      \node[box,fill=black] at (7,7){};
      \node[box,fill=red] at (7,6){};

      \draw[thick,color=green] (7,5.5) -- (7,3.5);
      \draw[thick,color=green,dashed] (7.5,6) -- (10.5,6);
      \draw[thick,color=green,dashed] (6.5,6) -- (-0.5,6);
      \draw[thick,color=green,dashed] (7,6.5) -- (7,10.5);

      \draw[thick,color=blue,] (7.2,5.5) -- (7.2,-0.5);
      \draw[thick,color=blue,] (7.5,6.2) -- (10.5,6.2);
      \draw[thick,color=blue,] (6.5,5.8) -- (-0.5,5.8);
      \draw[thick,color=blue,] (6.8,6.5) -- (6.8,10.5);

      \draw[thick,color=red,dashed] (6.8,5.5) -- (6.8,-0.5);
      \draw[thick,color=red,dashed] (7.5,5.8) -- (10.5,5.8);
      \draw[thick,color=red,] (6.5,6.2) -- (5.5,6.2);
      \draw[thick,color=red,] (7.2,6.5) -- (7.2,6.5);

    \end{tikzpicture}
  \end{center}
  \caption{Rays cast from the snake head. Green rays are the apple rays, red
    rays are the snake rays, and blue rays are the wall rays. If a ray is dashed,
  then it did not hit anything.}
  \label{fig:snake_rays}
\end{figure}

Once each ray has been cast, we pass the reciprocal of the distance to the
neural network. For example the down apple ray in figure \ref{fig:snake_rays},
would have a distance of $2$ since it travels two spaces before hitting the
apple. Thus the network would get a value of $\frac{1}{2}$. This is done so
that closer values are larger, and thus can easily be viewed as more important.

We also know that the output of the snake must be one of four values; Up, Down,
Left, or Right. Using this we constructed a neural network with $12$ input
neurons and $4$ output neurons. Most of the tests that we made were done
without any hidden layers, but it is also possible to insert hidden layers as
desired. The architecture of the network is demonstrated in figure
\ref{fig:snake_0layer}.

\begin{figure}[htpb]
  \begin{center}
    \begin{tikzpicture}[scale=1, transform shape]
      \node[circle,fill=black] (d00) at (0,-2.75) {};
      \node[circle,fill=black] (d01) at (0,-2.25) {};
      \node[circle,fill=black] (d02) at (0,-1.75) {};
      \node[circle,fill=black] (d03) at (0,-1.25) {};
      \node[circle,fill=black] (d04) at (0,-0.75) {};
      \node[circle,fill=black] (d05) at (0,-0.25) {};
      \node[circle,fill=black] (d06) at (0,0.25) {};
      \node[circle,fill=black] (d07) at (0,0.75) {};
      \node[circle,fill=black] (d08) at (0,1.25) {};
      \node[circle,fill=black] (d09) at (0,1.75) {};
      \node[circle,fill=black] (d010) at (0,2.25) {};
      \node[circle,fill=black] (d011) at (0,2.75) {};
      \node[circle,fill=black] (d10) at (5,-1.5) {};
      \draw (d00) -- (d10);
      \draw (d01) -- (d10);
      \draw (d02) -- (d10);
      \draw (d03) -- (d10);
      \draw (d04) -- (d10);
      \draw (d05) -- (d10);
      \draw (d06) -- (d10);
      \draw (d07) -- (d10);
      \draw (d08) -- (d10);
      \draw (d09) -- (d10);
      \draw (d010) -- (d10);
      \draw (d011) -- (d10);
      \node[circle,fill=black] (d11) at (5,-0.5) {};
      \draw (d00) -- (d11);
      \draw (d01) -- (d11);
      \draw (d02) -- (d11);
      \draw (d03) -- (d11);
      \draw (d04) -- (d11);
      \draw (d05) -- (d11);
      \draw (d06) -- (d11);
      \draw (d07) -- (d11);
      \draw (d08) -- (d11);
      \draw (d09) -- (d11);
      \draw (d010) -- (d11);
      \draw (d011) -- (d11);
      \node[circle,fill=black] (d12) at (5,0.5) {};
      \draw (d00) -- (d12);
      \draw (d01) -- (d12);
      \draw (d02) -- (d12);
      \draw (d03) -- (d12);
      \draw (d04) -- (d12);
      \draw (d05) -- (d12);
      \draw (d06) -- (d12);
      \draw (d07) -- (d12);
      \draw (d08) -- (d12);
      \draw (d09) -- (d12);
      \draw (d010) -- (d12);
      \draw (d011) -- (d12);
      \node[circle,fill=black] (d13) at (5,1.5) {};
      \draw (d00) -- (d13);
      \draw (d01) -- (d13);
      \draw (d02) -- (d13);
      \draw (d03) -- (d13);
      \draw (d04) -- (d13);
      \draw (d05) -- (d13);
      \draw (d06) -- (d13);
      \draw (d07) -- (d13);
      \draw (d08) -- (d13);
      \draw (d09) -- (d13);
      \draw (d010) -- (d13);
      \draw (d011) -- (d13);
    \end{tikzpicture}
  \end{center}
  \caption{Architecture of the snake AI neural network.}
  \label{fig:snake_0layer}
\end{figure}

Using this network architecture, there will be $48$ weights in the weight
matrix, and $4$ bias values in the bias vector. This means that there will be a
total of $52$ values that must be optimized.


\subsection{Training Network with Genetic Algorithm}

To optimize weights of a neural network, one must have training data, and the
answer key to that data. For situations like a game of snake. It is impossible
to know which direction it should go given every game state, so we are unable
to optimize a neural network in the classical method. This is why we implement
a genetic algorithm to optimize the neural network.

We construct a population of chromosomes, where each chromosomes has 52 genes.
We define a method for the conversion from the list of genes in the chromosome
to a neural network. The process is outlined below.

\begin{align*}
  \text{Chromo}=\left[x_1,\ldots,x_{52}\right]\implies
  W=\begin{bmatrix}
    x_1 & x_2 & \ldots & x_{12}\\
    x_{13} & x_{14} & \ldots & x_{24}\\
    x_{25} & x_{26} & \ldots & x_{36}\\
    x_{37} & x_{38} & \ldots & x_{48}\\
    \end{bmatrix},\quad B=\begin{bmatrix}
    x_{49} \\ x_{50} \\ x_{51} \\ x_{52}
  \end{bmatrix}
\end{align*}

For the evaluation stage of the genetic algorithm, each chromosome is converted
into a neural network, and it the plays the game of snake. The score returned
from that game is the fitness of the chromosome. Since the game has some
randomness in the generation of the apples. We evaluate each chromosome $5$
times, and average the scores to be the fitness. Then the rest of the genetic
algorithm proceeds as nominal, selecting the best chromosomes of the
population. After 20-50 generations, the network has usually made considerable
progress, and the learning curve has begun to plateau.

In the future it would be beneficial to experiment with additional layers, and
how having more layers of different sizes would effect the fitness of the
neural networks produced by the genetic algorithm.

\nocite{*}
\bibliographystyle{alpha}
\bibliography{main}

\end{document}

