\documentclass[12pt]{amsart}
\usepackage{amsmath}
\usepackage{csquotes}
\usepackage{enumitem}
\usepackage{hanging}
\usepackage[margin=1.5in]{geometry}

\title{Discussion 4}
\author{Arden Rasmussen}
\date{\today}

\begin{document}
\maketitle

\par\noindent\rule{\textwidth}{0.4pt}

\begin{hangparas}{.25in}{1}
  Appiah, Kwame Anthony. "Whose Culture Is It, Anyway?" in
  \textit{Cosmopolitanism: Ethics in a World of Strangers}, 115-135, 179-180.
  New York, W.W. Nortan \& Company, 2006.
\end{hangparas}

\par\noindent\rule{\textwidth}{0.4pt}

This article is about the ownership of artwork. The main debate of the author
is if art should belong to the nation of origin, or if it belongs to humanity
as a whole. And if it belongs to the nation, which nation is that. Since most
nations have since collapsed, then the modern nation that resides in the same
reason has had nothing directly to do with the art, so what gives them
additional power of control over the art. The author concludes that there is
not much of a better way of managing ownership, than to uses the land that it
was discovered on.

A second main point of the article is if art that has already been stolen or
removed from a nation, by either legal or illegal means, should be returned.
The author believes that not all of it should be returned. This was primarily
to diversify the worlds artistic knowledge, and provide people around the world
with the aspects of one cultures artwork.

I found that I really agreed with the author. I think that art should be
distributed around the world. Imagine if one wanted to seem Greek sculpture or
pottery, and the only place in the world was in greece. I think that would be
absurd, every culture possesses the most knowledge about their own culture, and
should share that culture with the rest of the world, to educate other
populations about their history.

I understand the importance of the finances of art, but personally I feel that
it is exceedingly important to share artwork with different cultures, so that
everyone can achieve some insight into the past.

\textbf{Are there any incentives to bring stolen artwork out of private
collections, so that they may be enjoyed by a wider population?}

\par\noindent\rule{\textwidth}{0.4pt}

Words: 274

\par\noindent\rule{\textwidth}{0.4pt}

\end{document}
